Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-10 papers/FX/draft.tex
Revised the draft.
Student's t with log-utility is solved.

Routledge and Zin \cite{routledge2010generalized} assumed
a power-law utility function of $C$:
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For our discussion it suffices that $u(\cdot)$ is
increasing and concave. Before proceeding any further, it is worth
stating the following simple observation:
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x; \theta)$ parameterized by
  $\theta$ is defined on $x \in (a, b)$, $a, b \in \mathbb R \cup
  \{-\infty, \infty\}$, and in addition $F(x; \theta)$ has density
  function $f(x; \theta)$. Assume function $h(\cdot)$ is defined on
  $(a, b)$, $X \sim F$, $\E h(X) < \infty$ and $\forall x \in (a, b)$
  \[
  \left| \pd{f(x, \theta)}{\theta} \right| < \infty
  \]
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} < 0
    \]
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} < 0
    \]
  \end{enumerate}
\end{lemma}
\begin{proof}
  Clearly
  \begin{eqnarray*}
    && \pd{\E h(X)}{\theta} \\
    &=& \int_a^b h(x) \pd{f}{\theta}(x, \theta) dx \\
    &=& \underbrace{\int_a^{x_0} h(x) \pd{f}{\theta}(x, \theta) dx}_{I_1}
    + \underbrace{\int_{x_0}^b h(x) \pd{f}{\theta}(x, \theta) dx}_{I_2}
  \end{eqnarray*}
  \begin{enumerate}
  \item When $h(x)$ is decreasing on $(a, b)$ and $\pd{f}{\theta}(x,
    \theta) > 0$ on $(a, x_0)$
    \[
    I_1 > h(x_0) \int_a^{x_0} \pd{f}{\theta}(x, \theta) dx
    \]
    Similarly, because $\pd{f}{\theta}(x, \theta) < 0$ for $x \in (x_0, b)$ and
    $h(x)$ is decreasing, we have
    \begin{eqnarray*}
      I_2 &=& \int_{x_0}^b -h(x_0)
      \left|\pd{f}{\theta}(x, \theta) \right| dx \\
      &>& -h(x_0)
      \int_{x_0}^b \left| 
        \pd{f}{\theta}(x, \theta)
      \right| dx
    \end{eqnarray*}
    Finally we have
    \begin{eqnarray*}
      && \pd{\E h(X)}{\theta} \\
      &=& I_1 + I_2 \\
      &>& h(x_0) \int_a^b \pd{f}{\theta}(x, \theta) dx \\
      &=& h(x_0) \opd{\theta} \int_a^b f(x, \theta) dx \\
      &=& h(x_0) \opd{\theta} 1 = 0
    \end{eqnarray*}
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$
    \begin{eqnarray*}
      I_1 &=&
      \int_a^{x_0} -h(x)
      \left| \pd{f}{\theta}(x, \theta) \right| dx \\
      &>&
      -h(x_0) \int_a^{x_0}
      \left| \pd{f}{\theta}(x, \theta) \right| dx
    \end{eqnarray*}
    and obviously
    \[
    I_2 > h(x_0) \int_{x_0}^b
    \pd{f}{\theta}(x, \theta) dx
    \]
    So
    \[
    \pd{\E h(X)}{\theta}
    = I_1 + I_2
    > h(x_0) \opd{\theta} \int_a^b f(x, \theta) dx = 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(x_0, b)$

    Obviously
    \[
    I_1 = \int_a^{x_0} h(x) \pd{f}{\theta}(x, \theta) dx
    < h(x_0) \int_a^{x_0} \pd{f}{\theta}(x, \theta) dx
    \]
    and
    \begin{eqnarray*}
      I_2 &=& \int_{x_0}^b h(x) \pd{f}{\theta}(x, \theta) dx \\
      &<& -h(x_0) \int_{x_0}^b \left| \pd{f}{\theta}(x, \theta) \right| dx \\
    \end{eqnarray*}
    Thus
    \[
    \pd{\E h(X)}{\theta}
    = I_1 + I_2
    < h(x_0) \opd{\theta} \int_a^b f(x, \theta) dx = 0
    \]
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$

    In this case
    \begin{eqnarray*}
      I_1 &=& \int_a^{x_0} h(x) \pd{f}{\theta}(x, \theta) dx \\
      &<& -h(x_0) \int_a^{x_0} \left| \pd{f}{\theta}(x, \theta) \right| dx
    \end{eqnarray*}
    And
    \begin{eqnarray*}
      I_2 &=& \int_{x_0}^b h(x) \pd{f}{\theta}(x, \theta) dx \\
      &<& h(x_0) \int_{x_0}^b \pd{f}{\theta}(x, \theta) dx
    \end{eqnarray*}
    So
    \[
    \pd{\E h(X)}{\theta}
    = I_1 + I_2
    < h(x_0) \opd{\theta} \int_a^b f(x, \theta) dx = 0
    \]
  \end{enumerate}
\end{proof}

Now for simplicity we assume the investor initially has one unit of
wealth. Let $r > 0$ be the return on the risk free state bond and $X$
be the return on equity. Portfolio weights are $\left(1-\phi\right)$
and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  C = (1 - \phi) e^r + \phi e^X
\end{equation}
Equation \eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q(r, \phi) &:=& \ln \left( {
    \delta v - (1 - \phi) e^r
    \over
    \phi
} \right) = \ln\left(
e^r + {\delta v - e^r \over \phi}
\right)
\end{eqnarray*}
Note $C < \delta v$ implies
\[
X < q(r, \phi)
\]
Hereafter we abbreviate $q(r, \phi)$ to just $q$. 
Naturally, if an agent invests in a risky asset instead of a riskless
bond, he expects to obtain a higher return from the risky asset than
he is guarranteed from the riskless bond. In our notation,
this means $\delta v > e^r$, which implies $q(r, \phi) > r > 0$.
The right-hand-side of \eqref{eq:functional} is a functional of $\phi$
and the distribution function of $X$ via \eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot, \cdot)$, i.e.
\[
\mathcal U(F, \phi)
= 
\E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\]
In the rest of this section, we use $F(\cdot)$ to denote the
distribution function of $X$ and use $f(\cdot)$ to denote its density
function. Let
\[
G(F) = \max_{0 < \phi \leq 1} \mathcal U(F, \phi)
\]

\subsection{Pareto-distributed equity return}
In this section, we look into the situation when $X$ has a shifted
Pareto distribution. Assume
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  \alpha K^\alpha  p
  \int_{-\infty}^0
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \over (K - x)^{\alpha + 1}} dx
  \nonumber \\
  &&
  \beta K'^\beta (1 - p)
  \int_{0}^\infty
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx \nonumber \\
  &&
  - b u(\delta v) \left[
    1 - (1 - p) {
      K'^\beta
      \over
      (K' + q)^\beta
    }
  \right]
  \label{eq:xxie1.0}
\end{eqnarray}
\begin{theorem}
  \label{thrm:I}
  \[
  \pd{G(F)}{\alpha} (\alpha, \beta, K, K') > 0,
  \quad
  \pd{G(F)}{K} (\alpha, \beta, K, K') < 0
  \]
\end{theorem}

\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F)(\alpha, \beta, K, K') = \mathcal U(F, \hat\phi)(\alpha, \beta, K, K')
  \]
  It follows
  \begin{eqnarray}
    \pd{G(F)}{\alpha}
    &=&
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, \beta, K, K', \hat\phi)
    \nonumber \\
    && + \pd{\mathcal U(F, \phi)}{\phi}(\alpha, \beta, K, K', \hat\phi)
    \pd{\hat\phi}{\alpha}(\alpha, \beta, K, K')
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U(F, \phi)}{\phi}(\alpha, \beta, K, K', \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    && \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, \beta, K, K', \hat\phi)
    \\
    &=& p \opd{\alpha}\E[u((1 - \phi) e^r + \phi e^X) | X < 0]
  \end{eqnarray*}
  The function $u((1 - \phi) e^r + \phi e^X)$ is obviously increasing
  with $X$. Furthermore, the density function of $X | X < 0$ is ${1
    \over p} f(x; \alpha, K)$. It follows
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{\alpha} \\
    &=& \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, \beta, K, K', \hat \phi) &>& 0
  \end{eqnarray*}
  As for $\pd{G(\alpha, \beta, K, K')}{K}$, by the same argument as for
  $\pd{G(\alpha, \beta, K, K')}{\alpha}$, it suffices to show
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, \beta, K, K', \hat\phi) < 0
  \]
  We have
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, \beta, K, K', \hat\phi)
  = p \opd{K} \E \left[
    u((1 - \phi) e^r + \phi e^X)
    | X < 0
  \right] 
  \]
  and
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{K} \\
    &=& \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the third case of lemma \ref{lemma:I} we conclude
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, \beta, K, K', \hat\phi) < 0  
  \]
\end{proof}
Since $u(v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$ and decreasing with $K$, there is a curve of
equal preference on the plane of $(\alpha, K)$. Moving along this
curve in the direction of increasing $\alpha$, one expects the values
of $K$ to increase too, i.e. the estimated values of $\alpha$ and $K$
should appear positively correlated. This is indeed the case in some
real stock return data, e.g. the ``Energy'' and ``Information Technology''
sectors of S\&P 500 companies. This is illustrated in figures
\ref{fig:Energy_alpha_K} and \ref{fig:Information_Technology_alpha_K}.
The confidence bands of the Hill estimates of $\alpha$ of these
sectors are shown in figures \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower} and
\ref{fig:Information_Technology_lower}.

\subsection{Student's t-distributed equity return}
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume
\[
f(x; \nu) = c(\nu) \left(
  1 + {x^2 \over \nu}
\right)^{-(\nu + 1)/2}
\]
where $\nu > 1$ and
\[
c(\nu) = {
  \Gamma({\nu + 1 \over 2})
  \over
  \Gamma(\nu/2) \sqrt{\nu \pi}
}
\]
\begin{theorem}
  \[
  \pd{G(F)}{\nu} > 0
  \]
  where the distribution function $F(x, \nu)$ corresponds to the
  density function $f(x, \nu)$ defined above.
\end{theorem}
\begin{proof}
  By the same argument as in the proof of theorem \ref{thrm:I}, it
  suffices to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\nu}(\nu, \hat\phi) &>& 0
  \end{eqnarray*}
  where $\hat\phi$ is defined in \eqref{eq:xxie2}. We have
  \begin{eqnarray*}
    && \mathcal U(F, \phi) \\
    &=&
    \int_{-\infty}^\infty
    u[(1 - \phi) e^r + \phi e^x] (1 + b \1{x < q}) f(x, \nu) dx
  \end{eqnarray*}

@@

>>>>

Routledge and Zin \cite{routledge2010generalized} assumed
a power-law utility function of $C$:
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For our discussion it suffices that $u(\cdot)$ is
increasing and concave. Before proceeding any further, it is worth
stating the following simple observation:
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x; \theta)$ parameterized by
  $\theta$ is defined on $x \in (a, b)$, $a, b \in \mathbb R \cup
  \{-\infty, \infty\}$, and in addition $F(x; \theta)$ has density
  function $f(x; \theta)$. Assume function $h(\cdot)$ is defined on
  $(a, b)$, $X \sim F$, $\text{supp}(X) = (a,b)$,
  $\E h(X) < \infty$ and
  \begin{eqnarray*}
    \opd{\theta}\left[
      F(b) - F(a)
    \right] = 0 \\
    \left| \pd{f(x, \theta)}{\theta} \right| < \infty
    \quad \forall x \in (a, b)
  \end{eqnarray*}
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\pd{f}{\theta}$ satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\pd{\E h(X)}{\theta} < 0$. This immediately follows from applying
    1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    $\pd{f}{\theta}$ satisfies the same conditions of the 2nd case of
    lemma \ref{lemma:I}, $\pd{\E h(X)}{\theta} < 0$.
  \end{enumerate}
\end{remark}
Now for simplicity we assume the investor initially has one unit of
wealth. Let $r > 0$ be the return on the risk free state bond and $X$
be the return on equity. Portfolio weights are $\left(1-\phi\right)$
and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  C = (1 - \phi) e^r + \phi e^X
\end{equation}
Equation \eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q = q(r, \phi) &:=& \ln \left( {
      \delta v - (1 - \phi) e^r
      \over
      \phi
    } \right) = \ln\left(
    e^r + {\delta v - e^r \over \phi}
  \right)
\end{eqnarray*}
Note $C < \delta v$ implies $X < q$. Naturally, if an agent invests in
a risky asset instead of a riskless bond, he expects to obtain a
higher return from the risky asset than he is guarranteed from the
riskless bond. In our notation, this means $\delta v > e^r$, which
implies $q(r, \phi) > r > 0$. The right-hand-side of
\eqref{eq:functional} is a functional of $\phi$ and the distribution
function of $X$ via \eqref{eq:xxie1}. For convenience we denote it
$\mathcal U(\cdot, \cdot)$, i.e.
\begin{equation}
  \label{eq:U_functional}
  \mathcal U(F, \phi)
  = 
  \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\end{equation}
In the rest of this section, we use $F(\cdot)$ to denote the
distribution function of $X$ and use $f(\cdot)$ to denote its density
function. Let
\begin{equation}
  \label{eq:G_functional}
  G(F) = \max_{0 < \phi \leq 1} \mathcal U(F, \phi)  
\end{equation}

\subsection{Pareto-distributed equity return}
In this section, we look into the situation when $X$ has a shifted
Pareto distribution. Assume
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  \alpha K^\alpha  p
  \int_{-\infty}^0
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \over (K - x)^{\alpha + 1}} dx
  \nonumber \\
  &&
  \beta K'^\beta (1 - p)
  \int_{0}^\infty
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx 
  + \text{const.}
  % &&
  % - b u(\delta v) \left[
  %   1 - (1 - p) {
  %     K'^\beta
  %     \over
  %     (K' + q)^\beta
  %   }
  % \right]
  \label{eq:xxie1.0}
\end{eqnarray}
where the last term is a constant independent of $\phi$, $\alpha$ and $K$.
\begin{theorem}
  \label{thrm:I}
  Suppose functional $G(\cdot)$ is given as \eqref{eq:G_functional},
  function $u(\cdot)$ is increasing and differentiable, then
  \[
  \pd{G(F)}{\alpha} > 0,
  \quad
  \pd{G(F)}{K} < 0
  \]
\end{theorem}
Since $u(v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$ and decreasing with $K$, there is a curve of
equal preference on the plane of $(\alpha, K)$. Moving along this
curve in the direction of increasing $\alpha$, one expects the values
of $K$ to increase too, i.e. the estimated values of $\alpha$ and $K$
should appear positively correlated. This is indeed the case in some
real stock return data, e.g. the ``Energy'' and ``Information Technology''
sectors of S\&P 500 companies. This is illustrated in figures
\ref{fig:Energy_alpha_K} and \ref{fig:Information_Technology_alpha_K}.
The confidence bands of the Hill estimates of $\alpha$ of these
sectors are shown in figures \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower} and
\ref{fig:Information_Technology_lower}.

\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \mathcal U(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    \pd{G(F)}{\alpha}
    &=&
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    + \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat\phi)
    \pd{\hat\phi}{\alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    = \opd{\alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously increasing
  with $X$. It follows
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{\alpha} \\
    &=& \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for $\pd{G(F)}{K}$, by the same argument as for
  $\pd{G(F)}{\alpha}$, it suffices to show
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi)
  = \opd{K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{K} \\
    &=& \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}

\subsection{Student's t-distributed equity return}
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume
\[
f(x; \nu) = c(\nu) \left(
  1 + {x^2 \over \nu}
\right)^{-(\nu + 1)/2}
\]
where $\nu > 1$ and
\[
c(\nu) = {
  \Gamma({\nu + 1 \over 2})
  \over
  \Gamma(\nu/2) \sqrt{\nu \pi}
}
\]
\begin{lemma}
  \label{lemma:II}
  There exists $x_0 > 0$ such that $\pd{f}{\nu}(x_0, \nu) = 0$ and
  $\forall x \in (0, x_0), \pd{f}{\nu}(x, \nu) > 0$ and
  $\forall x \in (x_0, \infty), \pd{f}{\nu}(x, \nu) < 0$.
\end{lemma}

\subsubsection{log-utility function}
We first consider the case where the utility function is simply
$u(\cdot) = \ln(\cdot)$. This corresponds to the limiting case of
\eqref{eq:power_utility} as $\gamma \to 0$.
\begin{theorem}
  Suppose functional $G(\cdot)$ is given as \eqref{eq:G_functional},
  function $u(\cdot) = \ln(\cdot)$, then
  \[
  \pd{G(F)}{\nu} < 0
  \]
  where $F(x, \nu)$ is the Student's t-distribution function.
\end{theorem}
\begin{proof}
  By the same argument as in the proof of theorem \ref{thrm:I}, it
  suffices to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\nu}(\nu, \hat\phi) &<& 0
  \end{eqnarray*}
  where $\hat\phi$ is defined in \eqref{eq:xxie2}. We have
  \begin{eqnarray*}
    && \mathcal U(F, \phi) \\
    &=&
    \int_{-\infty}^\infty
    u[(1 - \phi) e^r + \phi e^x] (1 + b \1{x < q}) f(x, \nu) dx
  \end{eqnarray*}

@@

\appendix
\section{Proof of lemma \ref{lemma:I}}
\begin{proof}
  Clearly
  \begin{eqnarray*}
    && \pd{\E h(X)}{\theta} \\
    &=& \int_a^b h(x) \pd{f}{\theta}(x, \theta) dx \\
    &=& \underbrace{\int_a^{x_0} h(x) \pd{f}{\theta}(x, \theta) dx}_{I_1}
    + \underbrace{\int_{x_0}^b h(x) \pd{f}{\theta}(x, \theta) dx}_{I_2}
  \end{eqnarray*}
  \begin{enumerate}
  \item When $h(x)$ is decreasing on $(a, b)$ and $\pd{f}{\theta}(x,
    \theta) > 0$ on $(a, x_0)$
    \[
    I_1 > h(x_0) \int_a^{x_0} \pd{f}{\theta}(x, \theta) dx
    \]
    Similarly, because $\pd{f}{\theta}(x, \theta) < 0$ for $x \in (x_0, b)$ and
    $h(x)$ is decreasing, we have
    \begin{eqnarray*}
      I_2 &=& \int_{x_0}^b -h(x_0)
      \left|\pd{f}{\theta}(x, \theta) \right| dx \\
      &>& -h(x_0)
      \int_{x_0}^b \left| 
        \pd{f}{\theta}(x, \theta)
      \right| dx
    \end{eqnarray*}
    Finally we have
    \begin{eqnarray*}
      \pd{\E h(X)}{\theta}
      > h(x_0) \int_a^b \pd{f}{\theta}(x, \theta) dx
      = h(x_0) \opd{\theta} \int_a^b f(x, \theta) dx
      = 0
    \end{eqnarray*}
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$
    \begin{eqnarray*}
      I_1 &=&
      \int_a^{x_0} -h(x)
      \left| \pd{f}{\theta}(x, \theta) \right| dx \\
      &>&
      -h(x_0) \int_a^{x_0}
      \left| \pd{f}{\theta}(x, \theta) \right| dx
    \end{eqnarray*}
    and obviously
    \[
    I_2 > h(x_0) \int_{x_0}^b
    \pd{f}{\theta}(x, \theta) dx
    \]
    So
    \[
    \pd{\E h(X)}{\theta}
    = I_1 + I_2
    > h(x_0) \opd{\theta} \int_a^b f(x, \theta) dx = 0
    \]
  \end{enumerate}
\end{proof}

\section{Proof of lemma \ref{lemma:II}}
